Liptschiz

### 2024-02-20 lipschitz/valabstraction.tex
update plots

\hspace*{-20ex}

\begin{tikzpicture}
	\begin{axis}[	axis on top,
				set layers=default,
				xrange=-5:5,
				yrange=-2:2,
				unit vector ratio=1 1 1, scale=1.5,
				view={60}{50},
				]
		\addplot3[fill=blue,opacity=0.1, fill opacity=0.4] 
		coordinates {
	 (0,0,0) (-1,1,0) (-4,1,0) (-4,-1,0) (0,-1,0) (0,0,0)
		};

@@

\hspace*{-20ex}

\begin{tikzpicture}
	\begin{axis}[	axis on top,
		set layers=default,
		xrange=-5:5,
		yrange=-2:2,
		unit vector ratio=1 1 1, scale=1.5,
		view={35}{14},
		]
		\addplot3[ fill=blue,opacity=0.1, fill opacity=0.4] 
		coordinates {
			(0,0,0) (-1,1,0) (-4,1,0) (-4,-1,0) (0,-1,0) (0,0,0)
		};

>>>>

The following plot will show the above constraints:

\begin{tikzpicture}
	\begin{axis}[
		xlabel={$y_i$},
		ylabel={$\hat{y}_i$},
		xmin=-2, xmax=2,
		ymin=-2, ymax=2,
		axis lines=center,
		samples=100, 
	 unit vector ratio=1 1 1, scale=1.5, xtick   = {-2,2},
	 xticklabels = {$-\gamma_i$,$\gamma_i$},
	 yticklabels = {},
		]
		\addplot[blue, thick, fill=blue, fill opacity=0.4] {x} \closedcycle; 
		\addplot[blue, thick] {0};

			\node[label={above:$(-\gamma_i,-\gamma_i)$}] at (axis cs: -1.35, -2.1) {};

			\node[label={above:$(\gamma_i,\gamma_i)$}] at (axis cs: 1.45, 1.7) {};
	\end{axis}
\end{tikzpicture}

\vspace*{10ex}

\begin{tikzpicture}
	\begin{axis}[	axis on top, xlabel = \(x_i\),
		ylabel = {\(y_i\)}, zlabel = \(\hat{y}_i\),
				set layers=default,
	xmax = 4, xmin = -4,
ymax = 1, ymin = -1,		
zmax = 1, zmin = -1,
				unit vector ratio=1 1 1, scale=1.5,
				view={60}{50}, ytick   = {-1,0,1},
				yticklabels = {$-\gamma_i$,$0$,$\gamma_i$}, xtick = {0},
				xticklabels = {$0$}, ztick   = {-1,0,1},
				zticklabels = {$-\gamma_i$,$0$,$\gamma_i$},
				]
		\addplot3[fill=blue,opacity=0.1, fill opacity=0.4] 
		coordinates {
	 (0,0,0) (-1,1,0) (-4,1,0) (-4,-1,0) (0,-1,0) (0,0,0)
		};

@@

\begin{tikzpicture}
	\begin{axis}[	axis on top, xlabel = \(x_i\),
		ylabel = {\(y_i\)}, zlabel = \(\hat{y}_i\),
		set layers=default,
				xmax = 4, xmin = -4,
		ymax = 1, ymin = -1,		
				zmax = 1, zmin = -1,
		unit vector ratio=1 1 1, scale=1.5,  ytick   = {-1,0,1},
		yticklabels = {$-\gamma_i$,$0$,$\gamma_i$}, xtick = {0},
		xticklabels = {$0$}, ztick   = {-1,0,1},
		zticklabels = {$-\gamma_i$,$0$,$\gamma_i$},
		view={35}{14},
		]
		\addplot3[ fill=blue,opacity=0.1, fill opacity=0.4] 
		coordinates {
			(0,0,0) (-1,1,0) (-4,1,0) (-4,-1,0) (0,-1,0) (0,0,0)
		};
